Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-28 paper/current/main.tex
edit_gravity_part

We model the flux of authors between organizations, $f_{ij}$, using the gravity law. 
the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
Following the gravity law, the expected flux between two organizations is defined as follows,

\begin{equation}
	\label{eq:gravity_basic}
	f_{ij} = C*m_{i}m_{j}*f(r_{ij})
\end{equation}

@@

We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.

@@

The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
We follow standard practice and exclude from our analysis zero flows.

>>>>

We model the flux of authors between organizations, $f_{ij}$, using the gravity law. 
the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
Following the gravity law, the expected flux $\widetilde{f_{ij}}$ between two organizations is defined as follows,

@@

We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
To estimate parameters $C$, $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.

@@

where $f_{ij}$ is the real flux from dataset. The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
We follow standard practice and exclude from our analysis zero flows.
